### 2018-12-10 Sections/models_for_quantum_computation.tex
no message

@@

The analysis for AQC involve bounding the eigenvalue gap of a complicated many-body Hamiltonian, which is a notoriously difficult problem. Nevertheless, a number of examples are known where a gap between classical and quantum. For example, adiabatic QC can perform a process analogous to Grover's search algorithm, providing a quadratic speed up over the best classical algorithm. Here we look at a few explicit algorithms for which AQC is known to give a speed up.

>>>>

The adiabatic theorem forms the the backbone of AQC, which states that for a system initially prepared in an eigenstate of a time-dependent Hamiltonian $H(t)$, the evolution

\begin{align}
i \frac{\partial \ket{\psi(t)}}{\partial t} = H(t)\ket{\psi(t)}
\end{align}
\noindent will keep approximately to the instantaneous ground state, if $H(t)$ varies ``sufficiently slowly".

@@

The analysis for AQC involve bounding the eigenvalue gap of a complicated many-body Hamiltonian, which is a notoriously difficult problem. Nevertheless, a number of examples are known where a gap between classical and quantum. 
These include:

\emph{The adiabatic quantum Grover algorithm} - as its name suggest, this is the adiabatic version of Grover's search algorithm \cite{}. The initial Hamiltonian is $H_0 = \openone - \ket{\phi}\bra{\phi}$, where $\ket{\phi}$ is the univorm superposition state $ \ket{+}^{\otimes n}. $
The final Hamiltonian is given by $H_1 = \openone - \ket{m}\bra{m}$, where $ \ket{m}$ is the marked item we are searching for.

\emph{Adiabatic Deutsch-Joza algorithm} - Given a function $f:\{0,1 \}^n \rightarrow {0,1}$ which is either constant or balanced, the Deutsch-Joza algorithm \cite{} can determine which type of function it is with a quantum speedup.

\emph{}

\emph{Adiabatic PAGERANK algorithm} - the PAGERANK vector is a crucial tool in data mining and information retrival, used by the Google search engine. The current algorithm outperforms all known current classical algorithms by a polynomial or even exponential speedup, but better future classical algorithms have not been ruled out.

\comment{Something about universality}
